Untitled

### 2018-08-17 PaperCode.Rmd
Don't destroy everything Postcodes
Going to change the postocde systme to one that is much simpler and uses a more easily maintainable dataset

```{r}
DataCover <-DATAdf  %>%
                #filter(!is.na(LAD11NM)) %>%
  summarise(
           'LADs' = length(unique(DATAdf$LAD11CD)), 
           '% of all LADs' = length(unique(DATAdf$LAD11CD))/length(unique(EW2$LAD11CD))*100,
           LUPs = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           '% of all Homes' = Homes/sum(EW2$Homes)*100,
           Population = sum(Pop, na.rm= T),
           '% of total population' = Population/sum(EW2$Pop)*100) %>%
  mutate_if(.<1, funs(signif(.,3))) %>%
  mutate_if(.>1, as.integer) %>%
  mutate_all(as.character) %>% 
  gather

@@

@@

 test2 <- test %>%
   select(LAD11CD, Predres, counts) %>%
   spread(key = Predres, value = counts, fill = 0)%>%
   mutate(FractCorrect = `TRUE`/200) %>%
   left_join(LADRefAverages %>% select(-Afford, -Affordsd, -HighLUP)) %>%
   left_join(select(LADMean,LAD11CD, HomesMedian, MedianDiff, Ego1TourismDens )) %>%
   mutate(PercDiff = (MedianDiff-HomesMedian)/HomesMedian)

>>>>

```{r}
DataCover <-DATAdf  %>%
                #filter(is.na(MSOA11CD)) %>%
  summarise(
           'LADs' = length(unique(DATAdf$LAD11CD)), 
           '% of all LADs' = length(unique(DATAdf$LAD11CD))/length(unique(EW2$LAD11CD))*100,
           LUPs = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           '% of all Homes' = Homes/sum(EW2$Homes)*100,
           Population = sum(Pop, na.rm= T),
           '% of total population' = Population/sum(EW2$Pop)*100) %>%
  mutate_if(.<1, funs(signif(.,3))) %>%
  mutate_if(.>1, as.integer) %>%
  mutate_all(as.character) %>% 
  gather

@@

#lost LUPS

LostLowUse <- DATAdf %>%
  filter(is.na(MSOA11CD)) %>%
  group_by(LAD11CD) %>%
  summarise(Lost = sum(LowUse)) %>%
  arrange(-Lost) %>%
  mutate(cumsum = cumsum(Lost),
         cumperc = cumsum/sum(Lost))

sum(LostLowUse$Lost)

ONSPD <- read_csv(file.path("/home/jonno/Dropbox/SSE/Empty Homes/ONSPD",
                            "ONS_Postcode_Directory_Latest_Centroids.csv"))

LADconv <- read_csv(file.path(AddGeog, 
                              "Local_Authority_Districts_December_2016_Names_and_Codes_in_the_United_Kingdom.csv")) %>%
  select(LAD11CD=LAD16CD, LAD11NM = LAD16NM)

test <- ONSPD %>%
  select(Postcode = pcd, LSOA11CD = lsoa11, MSOA11CD = msoa11, LAD11CD = oslaua, OA11CD = oa11,Country_code = ctry, Region =  rgn) %>%
  filter(grepl("(E92000001)|(W92000004)", Country_code)) %>%
  left_join(LADconv) %>%
  filter(!is.na(LSOA11CD))

test2 <- test  %>%
  filter(is.na(LSOA11CD))

map_dbl(.x = 1:ncol(test), ~{

  test %>% pull(.x) %>% is.na %>% sum

@@

 test2 <- test %>%
   select(LAD11CD, Predres, counts) %>%
   spread(key = Predres, value = counts, fill = 0) %>%
   mutate(FractCorrect = `TRUE`/200) %>%
   left_join(LADRefAverages %>% select(-Afford, -Affordsd, -HighLUP)) %>%
   left_join(select(LADMean,LAD11CD, HomesMedian, MedianDiff, Ego1TourismDens )) %>%
   mutate(PercDiff = (MedianDiff-HomesMedian)/HomesMedian) %>%
   left_join(LostLowUse)
